\textcolor{red}{Simple} connectome inference using partial correlation from imaging calcium signal

### 2014-06-17 article.tex
add some words about pca

\textcolor{red}{PCA?}

>>>>

\textcolor{red}{PCA?} Finally since there is a high correlation between neurons,
we filter some more noise through a principal component analysis. From the $|V|$
eigen vectors, we kept $80\%$ of the eigen vectors which have the largest eigen
value. In the context of the challenge, this assumption was deduced from ground
truth of provided networks.
